---
title: "Tidy Tuesday Week 25: African American History"
author: "Erin Chille"
date: "6/16/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The data related to this week's topic, african american history and Juneteenth, can be found [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-06-16/readme.md)

## Load necessary packages
```{r, message=FALSE}
library(maps)
library(dplyr)
library(tidyr)
library(sf)
library(ggplot2)
library(viridis)
```

## Get the Data

```{r, message=FALSE}
blackpast <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-16/blackpast.csv')
census <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-16/census.csv')
slave_routes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-16/slave_routes.csv')
african_names <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-16/african_names.csv')
```

## We will be making a bubble map to explore the ports

We want to do the ports that are fewer in number.
```{r}
head(african_names)
african_names$port_embark <- as.factor(african_names$port_embark)
african_names$port_disembark <- as.factor(african_names$port_disembark)
levels(african_names$port_embark)
levels(african_names$port_disembark)
```

There are 50-something port_embarks and only 5 port_disembarks, so we will be charting the port_disembark data.

### Get Lat/Long data for our port_disembark data.
```{r, warning=FALSE}
african_names.orig <- african_names

african_names$port_disembark <- gsub("Havana","23.1136,-82.3666",african_names$port_disembark) #Substitute town name for Lat,Long
african_names$port_disembark <- gsub("St. Helena","-15.555999,-5.415999", african_names$port_disembark) #Substitute town name for Lat,Long
african_names$port_disembark <- gsub("Bahamas unspecified","25.0443,-77.3504", african_names$port_disembark) #Substitute town name for Lat,Long
african_names$port_disembark <- gsub("Freetown", "8.4657,-13.2317", african_names$port_disembark) #Substitute town name for Lat,Long
african_names$port_disembark <- gsub("Kingston, Jamaica", "18.0179,-76.8099", african_names$port_disembark) #Substitute town name for Lat,Long
african_names_LL <- separate(african_names, port_disembark, into = c("Lat", "Long"), sep=",") #Separate into two columns

african_names_LL$port_disembark <- african_names.orig$port_disembark

str(unique(african_names_LL$Lat)) #Check that there are five latitudes
str(unique(african_names_LL$Long)) #Check that there are five longitudes
```

### Plot data
```{r}
port_disembark <- african_names_LL[,c(3,9:10,13)]
port_disembark <- port_disembark %>% group_by(port_disembark) %>% mutate(Pop=n()) %>% select(-name) 
port_disembark <- port_disembark[!duplicated(port_disembark), ]
print(port_disembark)
```

Make the map!
```{r}
# ggplot() +
#   geom_polygon(data = port_disembark, aes(x=Long, y = Lat, group = port_disembark), fill="grey", alpha=0.3) +
#   geom_point( data=port_disembark, aes(x=Long, y=Lat, size=Pop, color=Pop)) +
#   #scale_size_continuous(range=c(1,12)) +
#   #scale_color_viridis(trans="log") +
#   #theme_void() + 
#   #ylim(50,59) + 
#   coord_map() 
```

